---
title: "Dang_Son_Lesson04"
author: "SID 105-215-636"
date: "Stats 20 Summer 20"
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: darkly
    highlight: espresso
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 4 

### 1.(a)

```{r}
mat <- matrix(c(18.1, 15.5, 14.7, 17.4, 12.6, 15.5, 15.2, 13.2), nrow = 2, ncol = 4, byrow = TRUE)
mat

```

### 1.(b)

```{r}
mat[,2] <- sqrt(mat[,2])
mat

```

### 1.(c)
```{r}
is.matrix(mat[-1, -4])
is.vector(mat[-1, -4])
```
R returns a vector if I remove both the first row and the fourth column from (b) and store it as a new object

### 2.(a)

```{r}
load("Lesson3SU.RData")
ls()
lesson4 <- list(Q4B = Q4B, Q4C = Q4C,
                Q4d331 = Q4D331, Q4D430 = Q4D430,
                Q4D531 = Q4D531, Q4D614 = Q4D614)

```

### 2.(b)

```{r}
str(lesson4)
```

### 3

```{r}
MyModel <- lm(dist ~ speed, data = cars)
MySummary <- summary(MyModel)
mean(MySummary$residuals)

```

### 4

```{r}
typeof(MyModel)
typeof(MySummary)
class(MyModel)
class(MySummary)
```
The result of calling `plot(MyModel)` are plotting the linear regression model we generated from the data with *dist* as the dependent variable and *speed* as the independent variable. The plots are constructed based on the statistics from calling the functions `lm()`
I think the reason why calling `plot(MySummary)` did not generate plots is because even though they are both lists, they are different type of lists. `MyModel` is an object of class `lm` while `MySummary` is an object of class `summary.lm`. Therefore, it was probably because amongst al the different type of argument `plot()` accepts, list of class `lm` is one of them while list of class `summary.lm` isn't.
