---
title: "Dang_Son_Lab1"
author: "SID 105-215-636"
date: "6/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab 1 {.tabset}

## 1. Numeric Vectors

### A.
```{r}
atan(1 / 1:1000)
```
### B.
```{r}
x <- 1:1000
y <- atan(1 / x)
z <- 1 / tan(y)
```
### C.
```{r}
x == z
identical(x, z)
all.equal(x, z)
all.equal(x, z, tolerance = 1)
all.equal(x, z, tolerance = 0)
```
If the tolerance is set to 0, there needs to be no difference between the 2 arguments in order for the function to return TRUE. Even if the differences are smaller than the default value, which is close to 1.5e-8, the function will still not return TRUE.

## 2. Character and Logical Vectors

### A.
```{r}
a <- c("alpha", "bravo", "charlie", "delta", "echo")
```
### B.
```{r}
print(a[4])
```
### C.
```{r}
a <- c("Able", "Baker", "Charlie")
b <- c(T, T, F)
b + 3
d <- matrix(c(a,b),nrow=3)
str(b)
dim(b)
length(b)
str(d[, 2])
dim(d[, 2])
length(d[, 2])
typeof(d[, 2])
typeof(b)
```
The reason for the error that student gets for the line `d[,2] + 3` is because the type of vector extracted from `d[,2]` is character, not logical. Therefore, R does not know what to do with the `+` operation between a character type and a numeric type.


## 3. Matrices

### A.
```{r}
mat <- matrix((1:300), ncol = 3, byrow = TRUE)
head(mat)
```
### B.
```{r}
mat[2, ]
```
### C.
```{r}
mat[seq(from = 1, to = 100, by = 2), ]
```
### D.
First, on the tab **help**, I clicked on the *house symbol* to make sure I was at the Home page of the R Online Help System. Then I scrolled down to the **Reference** section and clicked on **Search Engine & Keywords**. Next, I put in the word **matrix** to look up all the functions that are related to matrices. Finally, I found on the lists of the function related to matrices that `Matrix.solve()` give you an inverse matrix of a square matrix.

### E.
```{r}
m <- matrix(c(1,5,1,6,8,4,23,6,2), ncol = 3, byrow = TRUE)
m
m_inverse <- solve(m)
m_inverse
zapsmall(m %*% m_inverse) # zapsmall() replaces values close to 0 with 0
```

## 4. Applications

### A.
It might be a bad idea to create objects named T or F because they are special names which R interprets as logical values TRUE and FALSE respectively. If you name an object either T or F, the object becomes ambiguous. In the case you use have object names either T or F, you might later forget and use T as TRUE and F as FALSE while T and F are no longer the logical values.

### B.
* When R computes `log(-1)`, it returns `NaN` because the expression is mathematically impossible to calculate. Therefore, R does not know what to do with the expression and returns `NaN` which is short for Not-a-Number
* When R computes `log(0)`, it returns `-Inf` because in the computer world, the number 0 is not the number 0 as what we, as human beings, think the number 0 is. In the computer world, the number 0 represent an extremely small number. Therefore, when we calculate log(0), the result is `-Inf` as $e^{-Inf}$ approaches 0.
* When R computes `log(Inf)`, it returns `Inf` because `Inf` represents a very big number which exceeds the ability of the computer to represent or display. The value `Inf` does however exists and is a real number. Therefore mathematically, `log(Inf)` is also a valid operation and the result is $e^{Inf}$ which approaches `Inf`

### C.
The student's code does not work because `log(tone2 > 0)` returns a numerical vector of the same length as tone2 and evaluates $log(j^{th}>0)$ with $j^{th}$ being either TRUE or FALSE which are interpreted as 1 or 0 in this case. Therefore the results are either 0 or -Inf.
```{r}
tone2 <- c(8, -1, 0, 1, 6, 7, 5, 3, 0, 9, Inf)
tone2[is.finite(tone2)]
```

### D.
```{r}
mat <- matrix(1:9, nrow=3, byrow=TRUE)
wins <- rbind(mat[1,], mat[2,], mat[3,],
              mat[,1], mat[,2], mat[,3],
              c(1, 5, 9), c(7, 5, 3))
wins
```


