---
title: "Dang_Son_Lesson02"
author: "SID 105-215-636"
date: "Stats 20 Summer 20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 4. {.tabset}

The {.tabset} gives you a way to organize your rendered html output.  It allows a reader to click instead of scroll.  You should delete this paragraph before you submit your lesson. The paragraph is just here to inform.

### A.

```{r}
## this is a comment in an R chunk
## type your R code after this line
print(paste("The result is:", 9 / 3 + 7 * 5 * 6 + 16 ))
```

### B.

```{r}
## this is a comment in an R chunk
## type your R code after this line
print(paste("The result is:", 24 / 3 * 4 - 3 + 7))
```

### C.

```{r}
## this is a comment in an R chunk
## type your R code after this line
print(paste("The result is:", 10 - 4 + 7 + 3 * (24 / 4)))
```

### D.

```{r}
## this is a comment in an R chunk
## type your R code after this line
print(paste("The result is:", sqrt(16) / 2 ^ 3))
```

### E.

```{r}
## this is a comment in an R chunk
## type your R code after this line
result <- log(0.3, base = exp(1)) #log(value, base)
print(paste("Log of 0.3 base e is:", result))
print(paste("Inverse of the result above is:", exp(1) ^ result))
```

### F.
* %% is modulus operator in R.
* 1:100 %% 3 will give you 100 elements with the values 1, 2, 0 recursively
* Similarly 1:100 %% 2 will give you 100 elements with the values 1, 0 recursively
* And 1:100 %% 5 will give you 100 elements with the value 1, 2, 3, 4, 0 recursively
* The & operator will interpret 0 as `FALSE` and any other value as `TRUE` before AND-ing two vectors.
  + `FALSE` means the value is divisible (because the result of the modulus operation is 0)
  + `TRUE` means the value is not divisible (because the result of the operation is not 0)
* Finally `1:100 %% 2 & 1:100 %% 3 & 1:100 %% 5` gives you a boolean vector of indices that are not divisible by 2, 3, and 5.
- Square bracket [ ] is to extract elements from a vector with a boolean vector of the same size.
```{r}
## this is a comment in an R chunk
## type your R code after this line
result <- (1:100) [1:100 %% 2 & 1:100 %% 3 & 1:100 %% 5]
result
```

### G.

```{r}
## this is a comment in an R chunk
## type your R code after this line
`an object` <- "this is an object"
`an object`
```

### H.

```{r}
## this is a comment in an R chunk
## type your R code after this line
4 < 12
12 > 4
12 <= 97
12 > 4
4 == 4
4 != 12
```

### I.

```{r}
## this is a comment in an R chunk
## type your R code after this line
value1 <- 4
result1 <- value1 * 2
result1 <- result1 + 2
result1 <- result1 / 2
result1 <- result1 + 12
result1 <- result1 - value1
result1

value2 <- 12
result2 <- value2 * 2
result2 <- result2 + 2
result2 <- result2 / 2
result2 <- result2 + 12
result2 <- result2 - value2
result2

value3 <- 97
result3 <- value3 * 2
result3 <- result3 + 2
result3 <- result3 / 2
result3 <- result3 + 12
result3 <- result3 - value3
result3
```

### J.

```{r}
trick2 <- function(x){
  (x * 2 + 2) / 2 + 12 - x
}
```

this is the test (remove the eval = FALSE when you are ready):

```{r}
trick2(-7)
trick2(18)
trick2(5000000)
```